### 2009-01-20 trunk/Papers/rmrs-08/rmrs.tex
typos; fixed figure; acknowledgments

A node variable $X$ is called a \emph{label} iff $\varphi$ contains an
atom of the form $\ep{X}{Y}{P}$ or $Y \qeq X$; it is an 
\emph{anchor} iff $\varphi$ contains an atom
of the form $\ep{Y}{X}{P}$ or $\ARG_S(X,i)$; and it is a
\emph{hole} iff $\varphi$ contains an atom of the form $\ARG_S(Y,X)$
or $X \qeq Y$.
\end{definition}

>>>>

A node variable $X$ is called a \emph{label} iff $\varphi$ contains an
atom of the form $\ep{X}{Y}{P}$ or $Y \dom X$; it is an 
\emph{anchor} iff $\varphi$ contains an atom
of the form $\ep{Y}{X}{P}$ or $\ARG_S(X,i)$; and it is a
\emph{hole} iff $\varphi$ contains an atom of the form $\ARG_S(Y,X)$
or $X \dom Y$.
\end{definition}
